% !TEX encoding = UTF-8 Unicode
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Friggeri Resume/CV
% XeLaTeX Template
% Version 1.0 (5/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX and the bibliography, if used,
% needs to be compiled with biber rather than bibtex.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[print]{gmorpain-cv} % Add 'print' as an option into the square bracket to remove colors from this template for printing

\addbibresource{bibliography.bib} % Specify the bibliography file to include publications

\begin{document}

\header{Grégoire }{Morpain}{23 years old, Graduated EPITECH in 2013, Systems Engineer / DevOps} % Your name and current job title/field

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
\section{Contact}
100 av. du Général Leclerc
75014 Paris
France
~
+33 (0) 6 30 92 23 48
~
\href{mailto:gregoire.morpain@gmail.com}{gregoire.morpain@gmail.com}
\href{https://www.linkedin.com/in/gregoiremorpain/en}{linkedin://gregoiremorpain}
\section{Languages}
French: native
English: full professional proficiency
%\section{Technologies {\color{red} $\varheartsuit$}}
\section{Technologies}
Puppet / Foreman
Varnish / HaProxy / Nginx
MongoDB / MySQL
C / C++
Perl / Ruby / PHP / Python
NodeJS / JavaScript
HTML5 / CSS3
\end{aside}

%----------------------------------------------------------------------------------------
%	PROFILE SECTION
%----------------------------------------------------------------------------------------

\section{Profile}
{I recently graduated from EPITECH after spending a year abroad in Concordia University, Montreal. I am specializing in systems and networks administration but I also have strong skills in development.}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}
\begin{entrylist}
%------------------------------------------------
\entry
{2008--2013}
{Expert {\normalfont in Information Technologies}}
{EPITECH, France}
{EPITECH has an innovative methodology based on projects, group work and autonomy which allowed me to turn my passion into a real expertise.}
%------------------------------------------------
\entry
{2012}
{Computer Science {\normalfont exchange student}}
{Concordia University, Canada}
{During two semesters at Concordia University, I had the opportunity to study computer science in this prestigious university.}
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Experience}
\begin{entrylist}
%------------------------------------------------
\entry
{Since 09/2012}
{BSO Network Solutions}
{Paris, France}
{\emph{Systems Engineer} \\
As an engineer at BSO, I am responsible for the outsourcing of client's platforms sometimes larger than 200 hosts. I am also in charge of the integration of new solutions, providing advices to the customer and doing level 2 \& 3 support.}
%------------------------------------------------
\entry
{07/2012--09/2012}
{Azendoo}
{Bordeaux, France}
{\emph{Mobile Developer (Mission)} \\
Using responsive web techniques, JavaScript and Backbone.js, I had to develop a cross platform mobile application. I learn to build great and optimized HTML5/CSS, good looking user interfaces and also to write efficient JavaScript code to ensure the best possible interactions with the application.}
%------------------------------------------------
\entry
{06/2011--08/2011}
{Azendoo}
{Bordeaux, France}
{\emph{Developer \& Administrator (Internship)} \\
I participated in the development of Azendoo web application, using the latest Web 2.0 standards and also to the implementation of the system’s architecture and deployment of the application in production.}
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Skills}
\ztable{System}{UNIX Systems / Lifecycle \& orchestration management}
\ztable{Virtualization}{VMWare, Xen}
\ztable{Monitoring}{Zabbix, Nagios}
\ztable{Network}{Brocade Loadbalancers \& Switches / Fortinet Firewall}

\end{document}